Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-19 WSSSPE2_report/WSSSPE2_review.tex
Section 11: minor changes.

WSSSPE actively used the online social network
Twitter, with hashtag ``\#WSSSPE''. There were substantially more tweets (messages)
during WSSSPE2 than WSSSPE1 or WSSSPE1.1. Some of the main points and highlights
in the meeting are shown in Table~\ref{tab:tweets}, which summarizes the
top \#WSSSPE tweets from the day of workshop.

>>>>

WSSSPE actively used the online social network Twitter, with hashtag
``\#WSSSPE''. There were substantially more tweets (messages) during the days of
the workshops WSSSPE2, WSSSPE1.1, and WSSSPE1. Out of about 670 tweets as of Apr
18, 2015, more than 225 were about WSSSPE2 and about 180 were posted during the
day of the workshop. Some of the main points and highlights in the meeting are
shown in Table~\ref{tab:tweets}, which summarizes the top \#WSSSPE tweets from
the day of workshop, selected by the metrics that number of retweets or
favourites larger than five and the sum of two measures greater than ten.
